Considering scale in multilayer animal social networks

### 2020-06-25 paper/manuscript.Rmd
N =

As the number of observations used to generate multilayer networks increased,
individuals became more connected and variance in metrics decreased.
Edge overlap increased across all three habitat
layers with increasing number of observations (Figure \@ref(fig:nobs) B).
Similarly, multidegree for all individuals increased quickly between 10 and 100
observations, and continued to increase until 1000 observations (Figure
\@ref(fig:nobs) C). Graph strength across individuals in all three habitat layers was highly
variable at low number of observations and variance decreased after ~100 observations
(Figure \@ref(fig:nobs) A). Given the observed trend of these multilayer metrics
decreasing in variance after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing social dynamics across
contexts.

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in social distance threshold. For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open). Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes. After 100 m, graph strength continued to increase at a slower rate. Foraging and open layers showed higher variation in graph strength between individuals while forest layers had less variation and lower mean graph strength.

<!-- Figure: metrics by land cover resolution -->
(ref:lcres) Varying spatial scale of land cover raster. For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open). A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m). D) Edge overlap of habitat layers across spatial resolutions. Open and forest layers show consistent edge overlap with increasing spatial resolution while foraging shows a sharp decline in edge overlap between 30 m and 600 m. Above 600 m, edge overlap in foraging layers is stable. E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution. Foraging layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution. Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest layers.

<!-- Figure: metrics by number of observations -->
(ref:nobs) Varying scale in number of observations. Multilayer networks were generated using a  subset of observations (10 - 1000 observations by steps of 10) of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open). A) Edge overlap increased for all habitat layers with increasing number of observations. Foraging and open layers had higher edge overlap than forest layers. B) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after ~200 observations. C) Multidegree increased for all individuals with increasing number of observations. Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).

<!-- Figure: Time window -->
(ref:temp) Varying temporal scale in multilayer networks. Multilayer networks were generated of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20). B) Ordinal network layers showing unweighted edges between individuals within time windows. Like edge overlap, individuals were more connected in time windows 1, 6-11, and 15-20, compared to 2-5 and 12-15. Number of individuals in each time window is reported below each layer. C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick black lines. Graph strength peaked in time window 9, with noticeable higher strength than the following year.

@@

(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut != 1, format(min(mindate), '%F')]` and `r DT[, format(max(datetime), '%F')]`. Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed. Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest, and open) informed by previous social, spatial and temporal scale analyses. Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).

>>>>

As the number of observations used to generate multilayer networks increased,
individuals became more connected and variance in metrics decreased.
Edge overlap increased across all three habitat
layers with increasing number of observations (Figure \@ref(fig:nobs) B).
Similarly, multidegree for all individuals increased quickly between 10 and 100
observations, and continued to increase until 1000 observations (Figure
\@ref(fig:nobs) C). Graph strength across individuals in all three habitat layers was highly
variable at low number of observations and variance decreased after ~100 observations
(Figure \@ref(fig:nobs) A). <!--TODO double check-->Since the variance in these 
multilayer metrics decreases after a certain number
of observations, this sensitivity method could be useful for determining the
number of observations necessary for sufficiently describing social dynamics
across contexts.

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in social distance threshold. For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (N =               `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open). Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes. After 100 m, graph strength continued to increase at a slower rate. Foraging and open layers showed higher variation in graph strength between individuals while forest layers had less variation and lower mean graph strength.

<!-- Figure: metrics by land cover resolution -->
(ref:lcres) Varying spatial scale of land cover raster. For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (N =               `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open). A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m). D) Edge overlap of habitat layers across spatial resolutions. Open and forest layers show consistent edge overlap with increasing spatial resolution while foraging shows a sharp decline in edge overlap between 30 m and 600 m. Above 600 m, edge overlap in foraging layers is stable. E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution. Foraging layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution. Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest layers.

<!-- Figure: metrics by number of observations -->
(ref:nobs) Varying scale in number of observations. Multilayer networks were generated using a  subset of observations (10 - 1000 observations by steps of 10) of caribou social associations (N =              `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` within three habitat layers (foraging, forest, and open). A) Edge overlap increased for all habitat layers with increasing number of observations. Foraging and open layers had higher edge overlap than forest layers. B) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after ~200 observations. C) Multidegree increased for all individuals with increasing number of observations. Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).

<!-- Figure: Time window -->
(ref:temp) Varying temporal scale in multilayer networks. Multilayer networks were generated of caribou social associations (N =              `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20). B) Ordinal network layers showing unweighted edges between individuals within time windows. Like edge overlap, individuals were more connected in time windows 1, 6-11, and 15-20, compared to 2-5 and 12-15. Number of individuals in each time window is reported below each layer. C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick black lines. Graph strength peaked in time window 9, with noticeable higher strength than the following year.

@@

(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut != 1, format(min(mindate), '%F')]` and `r DT[, format(max(datetime), '%F')]`. Individual caribou (N =              `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed. Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest, and open) informed by previous social, spatial and temporal scale analyses. Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).
